---
title: "2 - Passing objects"
author: "A bilingual case study"
---

```{r}
library(reticulate)
```

Activate a virtual environment

```{r}
use_virtualenv("modern_data", required = TRUE)

# Alternatively
# use_miniconda("~/modern_data", required = TRUE) 
```

Check active build

```{r}
py_config()
```

## Passing simple objects, scalars and vectors

### Py -> R 

Create and display a Python object in Python:

```{python eval = TRUE}
a = 3.14
a
```

Retreive and display a Python object in R:

```{r eval = TRUE}
py$a
```

### R -> Py 

Create and deisplay an R object in R:

```{r}
b <- 42
b
```

Retrieve and display an R object in Python

```{python}
r.b
```

## Passing data frames

### R -> Py 

An R `data.frame` in R:

```{r}
# A build-in data frame
head(PlantGrowth)
```

An R `data.frame` as a Python `DataFrame`. If you have pandas installed you'll see a `pandas.DataFrame` here. If not you'll get a `dict`

```{python}
r.PlantGrowth.head()
```

### Py -> R 

A Python `DataFrame` as an R `data.frame`

```{python}
import seaborn as sns

iris_df = sns.load_dataset('iris')
iris_df.head()
```

```{r}
# A build-in data frame
head(py$iris_df)
```

## Passing arrays

### Py -> R 

A Python NumPy `ndarray` in Python:

```{python eval = TRUE}
from sklearn.datasets import load_iris

iris = load_iris()
iris.data[:6]
```

A Python NumPy `ndarray` as an R `matrix`:

```{r eval = TRUE}
head(py$iris$data)
```

### R -> Py 

An R `matrix` in R:

```{r}
iris_data <- as.matrix(iris[-5])
head(iris_data)
```

An R `matrix` as a NumPy `ndarray`:

```{python}
r.iris_data[:6]
```

