---
title: "4 - Calling scripts"
author: "A bilingual case study"
---

```{r}
library(reticulate)
```

Activate a virtual environment

```{r}
use_virtualenv("modern_data", required = TRUE)

# Alternatively
# use_miniconda("~/modern_data", required = TRUE) 
```

Check active build

```{r}
py_config()
```

We have previously installed `scikit-learn` in the `modern_data` virtualenv. Let's look at a hello world example.

In contrast to the `3 - Using funcitons.Rmd` this time we'll just call all the Python commands by sourcing a script. 

```{r}
source_python("SVC_iris.py")
```

## Accessing python functions

Note: This is completely meaningless since were predicting the exact same data we used to train the model. It's just an exmaple of how to get things working, no a complete ML case study.

Importantly, Python functions and objects are available directly in the R environment, not via the `py` object. Thus, it is crucial to be aware of naming conflicts.

```{r}
clf$predict(r_to_py(iris[-5]))
```
